Adaptive Preregistration for Modelling

### 2024-09-22 preregistration_modelling.qmd
Remove duplicate preregistration item
qualify preregistration with explanatory clause

-   [ ] the ecological problem,
-   [ ] the decision problem (if relevant), including the decision-trigger and any regulatory frameworks relevant to the problem,
-   [ ] how the model will address the problem, being clear about the scope of the model i.e. is the model addressing the whole problem, or part of it? Are there any linked problems that your model should consider?
-   [ ] Ensure that you specify any focal taxa and study objectives,
-   [ ] Briefly outline the ecological problem and the decision-problem, including the decision-trigger and any regulatory frameworks relevant to the problem.
:::

@@

-   [ ] Document the identity, quantity and provenance of any data that will be used to develop, identify and test the model.
-   [ ] For each dataset, is the data open or publicly available?
-   [ ] How can the data be accessed? Provide a link or contact as appropriate, indicating any restrictions on the use of data.
-   [ ] Date of download, access, or future access.
-   [ ] Describe the source of the data - what entity originally collected this data? (National Data Set, Private Organisational Data, Own Lab Collection, Other Lab Collection, External Contractor, Meta-Analysis, Expert Elicitation, Other).
-   [ ] Codebook and meta-data. If a codebook or other meta-data is available, link to it here and / or upload the document(s).
-   [ ] Prior work based on this dataset - Have you published / presented any previous work based on this dataset? Include any publications, conference presentations (papers, posters), or working papers (in-prep, unpublished, preprints) based on this dataset you have worked on.
-   [ ] Unpublished Prior Research Activity - Describe any prior but unpublished research activity using these data. Be specific and transparent.
-   [ ] Prior knowledge of the current dataset - Describe any prior knowledge of or interaction with the dataset before commencing this study. For example, have you read any reports or publications about this data?
-   [ ] Describe how the data is arranged, in terms of replicates and covariates.

>>>>

-   [ ] the ecological problem,
-   [ ] the decision problem (if relevant), including the decision-trigger and any regulatory frameworks relevant to the problem,
-   [ ] how the model will address the problem, being clear about the scope of the model i.e. is the model addressing the whole problem, or part of it? Are there any linked problems that your model should consider?
-   [ ] Ensure that you specify any focal taxa and study objectives.
:::

@@

-   [ ] Document the identity, quantity and provenance of any data that will be used to develop, identify and test the model.
-   [ ] For each dataset, is the data open or publicly available?
-   [ ] How can the data be accessed? Provide a link or contact as appropriate, indicating any restrictions on the use of data.
-   [ ] Date of download, access, or expected timing offuture access.
-   [ ] Describe the source of the data - what entity originally collected this data? (National Data Set, Private Organisational Data, Own Lab Collection, Other Lab Collection, External Contractor, Meta-Analysis, Expert Elicitation, Other).
-   [ ] Codebook and meta-data. If a codebook or other meta-data is available, link to it here and / or upload the document(s).
-   [ ] Prior work based on this dataset - Have you published / presented any previous work based on this dataset? Include any publications, conference presentations (papers, posters), or working papers (in-prep, unpublished, preprints) based on this dataset you have worked on.
-   [ ] Unpublished Prior Research Activity - Describe any prior but unpublished research activity using these data. Be specific and transparent.
-   [ ] Prior knowledge of the current dataset - Describe any prior knowledge of or interaction with the dataset before commencing this study. For example, have you read any reports or publications about this data?
-   [ ] Describe how the data is arranged, in terms of replicates and covariates.
